\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\simpleResumeItem}[1]{
  \item\small{
  #1
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large PURUPURUNAME} & Email: \href{mailto:PURUPURUMAIL}{PURUPURUMAIL}\\
  Mobile: PURUPURUPHONE \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Profile}
      Polyglot software developer with 6+ years of experience in web development and big data.

      Writing Go for the better part of past 3 years.
      
      My top skills include Go, Java, Kafka, Cassandra, Spring Framework, Spark.

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {SRP Hyperplay}{}
      {Administrator}{Apr 2024 - Present}
      \resumeItemListStart
        \resumeItem{Senior Go Developer @ Kubeark}{
	  Developed core business products as part of a small but highly efficient team.

		\labelitemii \ Workflow engine design and implementation with state backed by Temporal.

                \labelitemii \ Project migrations from Python to Go.
	}
      \resumeItemListEnd
    \resumeSubheading
      {eSolutions}{}
      {Senior Software Developer}{Aug 2018 - Mar 2024}
      \resumeItemListStart
	\resumeItem{Senior Go Developer}{
	  Thanks to my previous experience I quickly became proficient in Go and fulfilled the following responsibilities for our clients:

          \labelitemii \ Application architecture and design. Setting up github and gitlab and github CI/CD, project structure, logging, dependency injection, error handling, api documentation, http clients, configuration, testing, data access patterns,
	  mocking, best practices and examples. 

	  \labelitemii \ Spearheaded Go development across teams through thorough POCs, presentations, workshops, demos, mentoring. 

	  \labelitemii \ Developed highly scalable solutions using AWS services such as SQS and DynamoDB to satisfy production requirements.
	}
        \resumeItem{Big Data}{
          Responsible for designing and implementing common big data requirements: 
	  
	  \labelitemii \ Acquisition via NiFi \& MiNiFi.

	  \labelitemii \ Storage using Cassandra, HDFS, Solr, Redis, RDBMS.

	  \labelitemii \ Processing using Kafka Streams, Kafka low level api consumer and producer, Kafka using Spring Cloud Stream.

	  \labelitemii \ Enrichment using Kafka, Spark with Scala.

	  \labelitemii \ Application development such as: adding customized continuous delivery and configurability to our edge data 
	  ingestion application, building a reliable Avro schema registry backed by Apache Zookeeper, adding features to an authentication and authorization API gateway.

	  \labelitemii \ Reduced memory allocation to 50\%, CPU usage to 50\% and message sizes to 15\% via a second Avro schema registry implementation. The implementation featured efficient thread synchronization using a low-level implementation equivalent of Go's singleflight, O(1) memory allocation and Kafka Topic backing, allowing for a 0 dependency deployment.
	  
          \labelitemii \ Monitored and debugged applications and data flows using ELK and Grafana.
          
          \labelitemii \ Advocated and delivered stream processing using Apache Kafka for significant code quality and 
	  performance improvements as a replacement to Spark batch processing.}

        \resumeItem{Web development - Java 8+ \& Typescript}{
	  Developed both front-end on Angular 7+ and backend on Spring Boot for multiple microservices used by a major retail chain. 

	  \labelitemii \ Developed complex queries using the JPA Criteria Api. 

	  \labelitemii \ Innovated by creating a library which simplifies the development experience for writing code that returns filtered lists for REST api's.

	  \labelitemii \ Tested backends using Spock, testcontainers as well as shell started docker containers. 

	  \labelitemii \ Worked on and introduced new team members to projects that use our custom framework for event sourcing and command query responsibility segregation.  

	  \labelitemii \ Configured and customized Angular Authentication and Authorization modules to fit multi-token requirements 
	  in multiple projects and across multiple OIDC client variants.

	\resumeItem{Others} {

	  \labelitemii \ Held a two day course on Kafka and how to use it with Spring Kafka.
	  
	  \labelitemii \ Held Java, Spring and Git courses to three generations of interns and mentored junior colleagues.

	  \labelitemii \ Used Agile across all projects either as Scrum or as Kanban.

	  \labelitemii \ Used Kubernetes, Docker, kustomize/helm together with bamboo/jenkins and Argo for most if not all projects and was repsonsible for further configuring CI/CD.

	  \labelitemii \ Knowledge and experience in using linux, bash, docker-compose, git and various command-line utilities.

	  \labelitemii \ Used docker, docker-compose, Dockerbuild, gitops, kubernetes across all projects for deployment, 
	  local testing and development.

	  \labelitemii \ Used microservices architecture extensively across all projects.

	  \labelitemii \ Took part in the interviewing process for Java internships and Go developer positions.
	}
}
      \resumeItemListEnd
      \newline\newline\newline
    \resumeSubheading
      {Soft Vision Media}{}
      {Java Developer}{Jul 2017 - Mar 2018}
      \resumeItemListStart
        \simpleResumeItem{
          Wrote data transformation code using XSLT and CSV parsers in order to integrate the company's product with various EDI providers. Built simple API integrations with various services.}
      \resumeItemListEnd
    \resumeSubheading
      {Eau de Web}{}
      {Full-Stack Drupal Developer Internship}{July 2016 - September 2016}
      \resumeItemListStart
        \simpleResumeItem{
          Built and integrated an IMAP module. Helped build the permission system for a custom collaborative business process flow. Integrated code with external APIs. Configured and customized simple websites. Maintained existing applications through tasks such as creating imports, exports, cleaning data, fixing bugs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Android Task Manager}
      {As part of a college project, using Dagger 2}
    \resumeSubItem{Web scraper}
      {Written using Java and JSoup with storage backed by mysql as part of a larger collaborative filtering and data analysis goal.}
    \resumeSubItem{Wordpress instance}
      {Customized and deployed a Wordpress blog on my personal bare-metal machine including bind9 DNS server installation and configuration.}
    \resumeSubItem{Blog}
      {Self-learned programming by writing a no-framework MVC architecture blog using php. Ported it to Symphony 2 later on.}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Programming Languages}{: Go, Java, Typescript, Scala, Groovy, SQL, Javascript}
    }
    \item{
      \textbf{Relevant technologies}{: Kafka, Spring Framework, Spark, Angular, Hadoop, Keycloak, Cassandra, NiFi, NodeRED, AWS SQS, AWS DynamoDB}
    }
    \item{
    \textbf{Languages}{: English - C1, German - beginner, French - beginner}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

